---
title: "20240312_MRS_M1"
author: "Yu Zhang"
date: "2024-03-06"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(readxl)
library(glmnet)
library(survey)
library(UpSetR)
```

# SOL Association Analysis
```{r}
sol_association_analysis <- function(pheno, mrs_df, id_col, outcome, cov_names, family_type = "gaussian") {
  mrsdat <- merge(pheno, mrs_df, by = id_col, all = TRUE)
  mrsdat <- na.omit(mrsdat)
  survey <- svydesign(
    id = ~PSU_ID, strata = ~STRAT,
    weights = ~WEIGHT_FINAL_NORM_OVERALL,
    data = mrsdat
  )
  mod <- svyglm(as.formula(paste(outcome, "~", paste0(outcome, "_MRS"), "+", paste(cov_names, collapse = " + "))),
    design = survey,
    na.action = na.omit,
    family = family_type
  )
  return(mod)
}
```

```{r}
result_list <- list()
coef_list <- list()
chem_list <- list()
```


# Insomnia

## Read data
```{r}

csv_files <- list()

csv_files[["b1"]] <- readRDS("Processed_metab_b1_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b1"]]), grep("SOL_ID", colnames(csv_files[["b1"]])))
colnames(csv_files[["b1"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b1"]])[col_chems])

csv_files[["b2"]] <- readRDS("Processed_metab_b2_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b2"]]), grep("SOL_ID", colnames(csv_files[["b2"]])))
colnames(csv_files[["b2"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b2"]])[col_chems])

rankNorm <- function(x){
  qnorm((rank(x, ties.method = "random", na.last = "keep")-0.5)/length(!is.na(x)))
}

chem_columns <- grep("chem", colnames(csv_files[["b1"]]), value = TRUE)

set.seed(89)
for (i in 1:length(chem_columns)){
  chem_i <- chem_columns[i]
  csv_files[["b1"]][,chem_i] <- rankNorm(csv_files[["b1"]][,chem_i])

  csv_files[["b2"]][,chem_i] <- rankNorm(csv_files[["b2"]][,chem_i])
}

pheno <- read.csv("metsleep_covariates_20200715.csv")


##############################
####### Outcome Define #######

pheno$Insomnia <- ifelse(pheno$WHIIRS >=9, 1, 0)
outcomes <- c("Insomnia")

##############################
##############################

covariates <- c("AGE", "GENDER", "CENTER", "Background")
pheno$CENTER <- factor(pheno$CENTER)
pheno$GENDER <- factor(pheno$GENDER)
pheno$Background <- factor(pheno$BKGRD1_C7)

design_vars <- c("ID", "STRAT", "PSU_ID", "WEIGHT_FINAL_NORM_OVERALL")

pheno <- pheno[,c(design_vars, outcomes, covariates)]
pheno <- pheno[!duplicated(pheno$ID),]

pheno$SOL_ID  <- as.character(pheno$ID)
```

## Batch 1

### Process Data
```{r}
dat_list <- list()

dat_list[["dat_b1"]] <- merge(pheno, csv_files[["b1"]], by = "SOL_ID", all.y = TRUE)

chem_columns <- grep("chem", colnames(dat_list[[1]]), value = TRUE)

process_data <- function(data, chem_columns) {
  data <- data[, c("SOL_ID", outcomes, "AGE", "GENDER",
                   "CENTER", "Background", chem_columns)]
  data <- data[complete.cases(data),]
  data$CENTER <- as.factor(data$CENTER)
  data$Background <- as.factor(data$Background)
  return(data)
}
dat_list[["dat_b1"]] <- process_data(dat_list[["dat_b1"]], chem_columns)
```

### LASSO
```{r}
lasso_selected <- function(data, chem_columns, outcome = outcomes) {
  x <- model.matrix(as.formula(paste(outcome, "~", paste(setdiff(colnames(data), c("SOL_ID", outcome)), collapse = "+"))), data = data)
  y <- data[,outcome]
  
  # apply penalty only on metabolites and not on other variables
  n_chem <- length(chem_columns)
  p.fac = c(rep(0, ncol(x) - n_chem), rep(1, n_chem))
  
  # CV
  set.seed(1997)
  kcvlasso <- cv.glmnet(x, y, nfolds = 5,
                        family = "binomial",
                        type.measure = "class",
                        penalty.factor = p.fac)
  
  ind_min <- which.min(kcvlasso$cvm)
  selected_lambda <- kcvlasso$lambda[ind_min]
  
  # lasso without cross validation
  set.seed(1997)
  lasso <- glmnet(x, y,
                  lambda = selected_lambda,
                  family = "binomial",
                  type.measure = "class",
                  penalty.factor = p.fac)
  
  lasso_beta <- lasso$beta
  mrs_coefs <- lasso_beta[grep("chem", rownames(lasso_beta)), "s0"]
  mrs_coefs <- mrs_coefs[which(mrs_coefs != 0)]
  
  return(mrs_coefs)
}

mrs_coefs <- lasso_selected(dat_list[[1]], chem_columns)

cat("There are ", length(mrs_coefs), " metablites selected into the MRS \n")

coef_list[[outcomes]] <- mrs_coefs
chem_list[[outcomes]] <- names(mrs_coefs)
```

### Construct MRS
```{r}
compute_mrs <- function(dataset, coef_set){
  row.names(dataset) <- dataset$SOL_ID
  tmp <- as.matrix(dataset[, names(coef_set)]) %*% coef_set
  colnames(tmp) <- outcomes
  tmp <- data.frame(tmp)
  tmp$SOL_ID <- rownames(tmp)
  mrs_b2 <- tmp
  row.names(mrs_b2) <- NULL
  return(mrs_b2)
}

mrs_b2 <- compute_mrs(csv_files[["b2"]], mrs_coefs)


# standardize MRS

mrs_b2[, 1] <- as.vector(scale(mrs_b2[, 1]))
colnames(mrs_b2)[1] <- paste0(outcomes, "_MRS")
```

### Association Test
```{r}
mod <- sol_association_analysis(pheno = pheno, mrs_df = mrs_b2, id_col = "SOL_ID", outcome = outcomes,
                            cov_names = covariates, family_type = "quasibinomial")
```

### store value
```{r}
summary_mod <- summary(mod)

# Extract Estimate and Standard Error for the first covariate
# The first covariate is at position 2 (as position 1 is the intercept)
estimate_first_covariate <- summary_mod$coefficients[2, "Estimate"]
stderr_first_covariate <- summary_mod$coefficients[2, "Std. Error"]
pvalue_first_covariate <- summary_mod$coefficients[2, "Pr(>|t|)"]

# Calculate 95% Confidence Interval
# Critical value for 95% CI under normal distribution is approximately 1.96
ci_low <- estimate_first_covariate - (1.96 * stderr_first_covariate)
ci_high <- estimate_first_covariate + (1.96 * stderr_first_covariate)

# Print the results
cat("Estimate for the first covariate:", estimate_first_covariate, "\n")
cat("95% CI for the first covariate: [", ci_low, ",", ci_high, "]\n")

dat_b2 <- merge(csv_files[["b2"]], pheno, by = "SOL_ID")
dat_b2 <- dat_b2[!is.na(dat_b2[[outcomes]]),]
size_b2 <- nrow(dat_b2)

mod_df <- data.frame(Exposures = outcomes, Sample_Size = nrow(dat_list[["dat_b1"]]), Sample_Size_b2 = size_b2, Est = exp(estimate_first_covariate),
                     CI_Lower = exp(ci_low), CI_Upper = exp(ci_high),
                     P_Value = pvalue_first_covariate, Metabolites = length(mrs_coefs))
result_list[[outcomes]] <- mod_df
```

# WHIIRS

## Read data
```{r}

csv_files <- list()

csv_files[["b1"]] <- readRDS("Processed_metab_b1_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b1"]]), grep("SOL_ID", colnames(csv_files[["b1"]])))
colnames(csv_files[["b1"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b1"]])[col_chems])

csv_files[["b2"]] <- readRDS("Processed_metab_b2_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b2"]]), grep("SOL_ID", colnames(csv_files[["b2"]])))
colnames(csv_files[["b2"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b2"]])[col_chems])

rankNorm <- function(x){
  qnorm((rank(x, ties.method = "random", na.last = "keep")-0.5)/length(!is.na(x)))
}

chem_columns <- grep("chem", colnames(csv_files[["b1"]]), value = TRUE)

set.seed(89)
for (i in 1:length(chem_columns)){
  chem_i <- chem_columns[i]
  csv_files[["b1"]][,chem_i] <- rankNorm(csv_files[["b1"]][,chem_i])

  csv_files[["b2"]][,chem_i] <- rankNorm(csv_files[["b2"]][,chem_i])
}


pheno <- read.csv("metsleep_covariates_20200715.csv")


##############################
####### Outcome Define #######


outcomes <- c("WHIIRS")

##############################
##############################

covariates <- c("AGE", "GENDER", "CENTER", "Background")
pheno$CENTER <- factor(pheno$CENTER)
pheno$GENDER <- factor(pheno$GENDER)
pheno$Background <- factor(pheno$BKGRD1_C7)

design_vars <- c("ID", "STRAT", "PSU_ID", "WEIGHT_FINAL_NORM_OVERALL")

pheno <- pheno[,c(design_vars, outcomes, covariates)]
pheno <- pheno[!duplicated(pheno$ID),]

pheno$SOL_ID  <- as.character(pheno$ID)
```

## Batch 1

### Process Data
```{r}
dat_list <- list()

dat_list[["dat_b1"]] <- merge(pheno, csv_files[["b1"]], by = "SOL_ID", all.y = TRUE)

chem_columns <- grep("chem", colnames(dat_list[[1]]), value = TRUE)

process_data <- function(data, chem_columns) {
  data <- data[, c("SOL_ID", outcomes, "AGE", "GENDER",
                   "CENTER", "Background", chem_columns)]
  data <- data[complete.cases(data),]
  data$CENTER <- as.factor(data$CENTER)
  data$Background <- as.factor(data$Background)
  return(data)
}
dat_list[["dat_b1"]] <- process_data(dat_list[["dat_b1"]], chem_columns)
```

### LASSO
```{r}
lasso_selected <- function(data, chem_columns, outcome = outcomes) {
  x <- model.matrix(as.formula(paste(outcome, "~", paste(setdiff(colnames(data), c("SOL_ID", outcome)), collapse = "+"))), data = data)
  y <- data[,outcome]
  
  # apply penalty only on metabolites and not on other variables
  n_chem <- length(chem_columns)
  p.fac = c(rep(0, ncol(x) - n_chem), rep(1, n_chem))
  
  # CV
  set.seed(1997)
  kcvlasso <- cv.glmnet(x, y, nfolds = 5,
                        family = "gaussian",
                        type.measure = "mse",
                        penalty.factor = p.fac)
  
  ind_min <- which.min(kcvlasso$cvm)
  selected_lambda <- kcvlasso$lambda[ind_min]
  
  # lasso without cross validation
  set.seed(1997)
  lasso <- glmnet(x, y,
                  lambda = selected_lambda,
                  family = "gaussian",
                  type.measure = "mse",
                  penalty.factor = p.fac)
  
  lasso_beta <- lasso$beta
  mrs_coefs <- lasso_beta[grep("chem", rownames(lasso_beta)), "s0"]
  mrs_coefs <- mrs_coefs[which(mrs_coefs != 0)]
  
  return(mrs_coefs)
}

mrs_coefs <- lasso_selected(dat_list[[1]], chem_columns)

cat("There are ", length(mrs_coefs), " metablites selected into the MRS \n")

coef_list[[outcomes]] <- mrs_coefs
chem_list[[outcomes]] <- names(mrs_coefs)
```

### Construct MRS
```{r}
compute_mrs <- function(dataset, coef_set){
  row.names(dataset) <- dataset$SOL_ID
  tmp <- as.matrix(dataset[, names(coef_set)]) %*% coef_set
  colnames(tmp) <- outcomes
  tmp <- data.frame(tmp)
  tmp$SOL_ID <- rownames(tmp)
  mrs_b2 <- tmp
  row.names(mrs_b2) <- NULL
  return(mrs_b2)
}

mrs_b2 <- compute_mrs(csv_files[["b2"]], mrs_coefs)


# standardize MRS

mrs_b2[, 1] <- as.vector(scale(mrs_b2[, 1]))
colnames(mrs_b2)[1] <- paste0(outcomes, "_MRS")
```

### Association Test
```{r}
mod <- sol_association_analysis(pheno = pheno, mrs_df = mrs_b2, id_col = "SOL_ID", outcome = outcomes,
                            cov_names = covariates, family_type = "gaussian")
```

### store value
```{r}
summary_mod <- summary(mod)

# Extract Estimate and Standard Error for the first covariate
# The first covariate is at position 2 (as position 1 is the intercept)
estimate_first_covariate <- summary_mod$coefficients[2, "Estimate"]
stderr_first_covariate <- summary_mod$coefficients[2, "Std. Error"]
pvalue_first_covariate <- summary_mod$coefficients[2, "Pr(>|t|)"]

# Calculate 95% Confidence Interval
# Critical value for 95% CI under normal distribution is approximately 1.96
ci_low <- estimate_first_covariate - (1.96 * stderr_first_covariate)
ci_high <- estimate_first_covariate + (1.96 * stderr_first_covariate)

# Print the results
cat("Estimate for the first covariate:", estimate_first_covariate, "\n")
cat("95% CI for the first covariate: [", ci_low, ",", ci_high, "]\n")

dat_b2 <- merge(csv_files[["b2"]], pheno, by = "SOL_ID")
dat_b2 <- dat_b2[!is.na(dat_b2[[outcomes]]),]
size_b2 <- nrow(dat_b2)

mod_df <- data.frame(Exposures = outcomes, Sample_Size = nrow(dat_list[["dat_b1"]]), Sample_Size_b2 = size_b2, Est = estimate_first_covariate,
                     CI_Lower = ci_low, CI_Upper = ci_high,
                     P_Value = pvalue_first_covariate, Metabolites = length(mrs_coefs))
result_list[[outcomes]] <- mod_df
```

# SLEA4

## Read data
```{r}

csv_files <- list()

csv_files[["b1"]] <- readRDS("Processed_metab_b1_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b1"]]), grep("SOL_ID", colnames(csv_files[["b1"]])))
colnames(csv_files[["b1"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b1"]])[col_chems])

csv_files[["b2"]] <- readRDS("Processed_metab_b2_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b2"]]), grep("SOL_ID", colnames(csv_files[["b2"]])))
colnames(csv_files[["b2"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b2"]])[col_chems])

rankNorm <- function(x){
  qnorm((rank(x, ties.method = "random", na.last = "keep")-0.5)/length(!is.na(x)))
}

chem_columns <- grep("chem", colnames(csv_files[["b1"]]), value = TRUE)

set.seed(89)
for (i in 1:length(chem_columns)){
  chem_i <- chem_columns[i]
  csv_files[["b1"]][,chem_i] <- rankNorm(csv_files[["b1"]][,chem_i])

  csv_files[["b2"]][,chem_i] <- rankNorm(csv_files[["b2"]][,chem_i])
}


pheno <- read.csv("metsleep_covariates_20200715.csv")
pheno <- lapply(pheno, function(x) ifelse(x == "", NA, x))
pheno <- as.data.frame(pheno)
pheno$SLEA4 <- as.numeric(as.character(pheno$SLEA4))
pheno$SLEA5 <- as.numeric(as.character(pheno$SLEA5))
pheno$SLEA6 <- as.numeric(as.character(pheno$SLEA6))
pheno$SLEA7 <- as.numeric(as.character(pheno$SLEA7))


##############################
####### Outcome Define #######


outcomes <- c("SLEA4")

##############################
##############################

covariates <- c("AGE", "GENDER", "CENTER", "Background")
pheno$CENTER <- factor(pheno$CENTER)
pheno$GENDER <- factor(pheno$GENDER)
pheno$Background <- factor(pheno$BKGRD1_C7)

design_vars <- c("ID", "STRAT", "PSU_ID", "WEIGHT_FINAL_NORM_OVERALL")

pheno <- pheno[,c(design_vars, outcomes, covariates)]
pheno <- pheno[!duplicated(pheno$ID),]

pheno$SOL_ID  <- as.character(pheno$ID)
```

## Batch 1

### Process Data
```{r}
dat_list <- list()

dat_list[["dat_b1"]] <- merge(pheno, csv_files[["b1"]], by = "SOL_ID", all.y = TRUE)

chem_columns <- grep("chem", colnames(dat_list[[1]]), value = TRUE)

process_data <- function(data, chem_columns) {
  data <- data[, c("SOL_ID", outcomes, "AGE", "GENDER",
                   "CENTER", "Background", chem_columns)]
  data <- data[complete.cases(data),]
  data$CENTER <- as.factor(data$CENTER)
  data$Background <- as.factor(data$Background)
  return(data)
}
dat_list[["dat_b1"]] <- process_data(dat_list[["dat_b1"]], chem_columns)
```

### LASSO
```{r}
lasso_selected <- function(data, chem_columns, outcome = outcomes) {
  x <- model.matrix(as.formula(paste(outcome, "~", paste(setdiff(colnames(data), c("SOL_ID", outcome)), collapse = "+"))), data = data)
  y <- data[,outcome]
  
  # apply penalty only on metabolites and not on other variables
  n_chem <- length(chem_columns)
  p.fac = c(rep(0, ncol(x) - n_chem), rep(1, n_chem))
  
  # CV
  set.seed(1997)
  kcvlasso <- cv.glmnet(x, y, nfolds = 5,
                        family = "gaussian",
                        type.measure = "mse",
                        penalty.factor = p.fac)
  
  ind_min <- which.min(kcvlasso$cvm)
  selected_lambda <- kcvlasso$lambda[ind_min]
  
  # lasso without cross validation
  set.seed(1997)
  lasso <- glmnet(x, y,
                  lambda = selected_lambda,
                  family = "gaussian",
                  type.measure = "mse",
                  penalty.factor = p.fac)
  
  lasso_beta <- lasso$beta
  mrs_coefs <- lasso_beta[grep("chem", rownames(lasso_beta)), "s0"]
  mrs_coefs <- mrs_coefs[which(mrs_coefs != 0)]
  
  return(mrs_coefs)
}

mrs_coefs <- lasso_selected(dat_list[[1]], chem_columns)

cat("There are ", length(mrs_coefs), " metablites selected into the MRS \n")

coef_list[[outcomes]] <- mrs_coefs
chem_list[[outcomes]] <- names(mrs_coefs)
```

### Construct MRS
```{r}
compute_mrs <- function(dataset, coef_set){
  row.names(dataset) <- dataset$SOL_ID
  tmp <- as.matrix(dataset[, names(coef_set)]) %*% coef_set
  colnames(tmp) <- outcomes
  tmp <- data.frame(tmp)
  tmp$SOL_ID <- rownames(tmp)
  mrs_b2 <- tmp
  row.names(mrs_b2) <- NULL
  return(mrs_b2)
}

mrs_b2 <- compute_mrs(csv_files[["b2"]], mrs_coefs)


# standardize MRS

mrs_b2[, 1] <- as.vector(scale(mrs_b2[, 1]))
colnames(mrs_b2)[1] <- paste0(outcomes, "_MRS")
```

### Association Test
```{r}
mod <- sol_association_analysis(pheno = pheno, mrs_df = mrs_b2, id_col = "SOL_ID", outcome = outcomes,
                            cov_names = covariates, family_type = "gaussian")
```

### store value
```{r}
summary_mod <- summary(mod)

# Extract Estimate and Standard Error for the first covariate
# The first covariate is at position 2 (as position 1 is the intercept)
estimate_first_covariate <- summary_mod$coefficients[2, "Estimate"]
stderr_first_covariate <- summary_mod$coefficients[2, "Std. Error"]
pvalue_first_covariate <- summary_mod$coefficients[2, "Pr(>|t|)"]

# Calculate 95% Confidence Interval
# Critical value for 95% CI under normal distribution is approximately 1.96
ci_low <- estimate_first_covariate - (1.96 * stderr_first_covariate)
ci_high <- estimate_first_covariate + (1.96 * stderr_first_covariate)

# Print the results
cat("Estimate for the first covariate:", estimate_first_covariate, "\n")
cat("95% CI for the first covariate: [", ci_low, ",", ci_high, "]\n")

dat_b2 <- merge(csv_files[["b2"]], pheno, by = "SOL_ID")
dat_b2 <- dat_b2[!is.na(dat_b2[[outcomes]]),]
size_b2 <- nrow(dat_b2)

mod_df <- data.frame(Exposures = outcomes, Sample_Size = nrow(dat_list[["dat_b1"]]), Sample_Size_b2 = size_b2, Est = estimate_first_covariate,
                     CI_Lower = ci_low, CI_Upper = ci_high,
                     P_Value = pvalue_first_covariate, Metabolites = length(mrs_coefs))
result_list[[outcomes]] <- mod_df
```

# SLEA5

## Read data
```{r}

csv_files <- list()

csv_files[["b1"]] <- readRDS("Processed_metab_b1_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b1"]]), grep("SOL_ID", colnames(csv_files[["b1"]])))
colnames(csv_files[["b1"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b1"]])[col_chems])

csv_files[["b2"]] <- readRDS("Processed_metab_b2_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b2"]]), grep("SOL_ID", colnames(csv_files[["b2"]])))
colnames(csv_files[["b2"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b2"]])[col_chems])

rankNorm <- function(x){
  qnorm((rank(x, ties.method = "random", na.last = "keep")-0.5)/length(!is.na(x)))
}

chem_columns <- grep("chem", colnames(csv_files[["b1"]]), value = TRUE)

set.seed(89)
for (i in 1:length(chem_columns)){
  chem_i <- chem_columns[i]
  csv_files[["b1"]][,chem_i] <- rankNorm(csv_files[["b1"]][,chem_i])

  csv_files[["b2"]][,chem_i] <- rankNorm(csv_files[["b2"]][,chem_i])
}


pheno <- read.csv("metsleep_covariates_20200715.csv")
pheno <- lapply(pheno, function(x) ifelse(x == "", NA, x))
pheno <- as.data.frame(pheno)
pheno$SLEA4 <- as.numeric(as.character(pheno$SLEA4))
pheno$SLEA5 <- as.numeric(as.character(pheno$SLEA5))
pheno$SLEA6 <- as.numeric(as.character(pheno$SLEA6))
pheno$SLEA7 <- as.numeric(as.character(pheno$SLEA7))


##############################
####### Outcome Define #######


outcomes <- c("SLEA5")

##############################
##############################

covariates <- c("AGE", "GENDER", "CENTER", "Background")
pheno$CENTER <- factor(pheno$CENTER)
pheno$GENDER <- factor(pheno$GENDER)
pheno$Background <- factor(pheno$BKGRD1_C7)

design_vars <- c("ID", "STRAT", "PSU_ID", "WEIGHT_FINAL_NORM_OVERALL")

pheno <- pheno[,c(design_vars, outcomes, covariates)]
pheno <- pheno[!duplicated(pheno$ID),]

pheno$SOL_ID  <- as.character(pheno$ID)
```

## Batch 1

### Process Data
```{r}
dat_list <- list()

dat_list[["dat_b1"]] <- merge(pheno, csv_files[["b1"]], by = "SOL_ID", all.y = TRUE)

chem_columns <- grep("chem", colnames(dat_list[[1]]), value = TRUE)

process_data <- function(data, chem_columns) {
  data <- data[, c("SOL_ID", outcomes, "AGE", "GENDER",
                   "CENTER", "Background", chem_columns)]
  data <- data[complete.cases(data),]
  data$CENTER <- as.factor(data$CENTER)
  data$Background <- as.factor(data$Background)
  return(data)
}
dat_list[["dat_b1"]] <- process_data(dat_list[["dat_b1"]], chem_columns)
```

### LASSO
```{r}
lasso_selected <- function(data, chem_columns, outcome = outcomes) {
  x <- model.matrix(as.formula(paste(outcome, "~", paste(setdiff(colnames(data), c("SOL_ID", outcome)), collapse = "+"))), data = data)
  y <- data[,outcome]
  
  # apply penalty only on metabolites and not on other variables
  n_chem <- length(chem_columns)
  p.fac = c(rep(0, ncol(x) - n_chem), rep(1, n_chem))
  
  # CV
  set.seed(1997)
  kcvlasso <- cv.glmnet(x, y, nfolds = 5,
                        family = "gaussian",
                        type.measure = "mse",
                        penalty.factor = p.fac)
  
  ind_min <- which.min(kcvlasso$cvm)
  selected_lambda <- kcvlasso$lambda[ind_min]
  
  # lasso without cross validation
  set.seed(1997)
  lasso <- glmnet(x, y,
                  lambda = selected_lambda,
                  family = "gaussian",
                  type.measure = "mse",
                  penalty.factor = p.fac)
  
  lasso_beta <- lasso$beta
  mrs_coefs <- lasso_beta[grep("chem", rownames(lasso_beta)), "s0"]
  mrs_coefs <- mrs_coefs[which(mrs_coefs != 0)]
  
  return(mrs_coefs)
}

mrs_coefs <- lasso_selected(dat_list[[1]], chem_columns)

cat("There are ", length(mrs_coefs), " metablites selected into the MRS \n")

coef_list[[outcomes]] <- mrs_coefs
chem_list[[outcomes]] <- names(mrs_coefs)
```

### Construct MRS
```{r}
compute_mrs <- function(dataset, coef_set){
  row.names(dataset) <- dataset$SOL_ID
  tmp <- as.matrix(dataset[, names(coef_set)]) %*% coef_set
  colnames(tmp) <- outcomes
  tmp <- data.frame(tmp)
  tmp$SOL_ID <- rownames(tmp)
  mrs_b2 <- tmp
  row.names(mrs_b2) <- NULL
  return(mrs_b2)
}

mrs_b2 <- compute_mrs(csv_files[["b2"]], mrs_coefs)


# standardize MRS

mrs_b2[, 1] <- as.vector(scale(mrs_b2[, 1]))
colnames(mrs_b2)[1] <- paste0(outcomes, "_MRS")
```

### Association Test
```{r}
mod <- sol_association_analysis(pheno = pheno, mrs_df = mrs_b2, id_col = "SOL_ID", outcome = outcomes,
                            cov_names = covariates, family_type = "gaussian")
```

### store value
```{r}
summary_mod <- summary(mod)

# Extract Estimate and Standard Error for the first covariate
# The first covariate is at position 2 (as position 1 is the intercept)
estimate_first_covariate <- summary_mod$coefficients[2, "Estimate"]
stderr_first_covariate <- summary_mod$coefficients[2, "Std. Error"]
pvalue_first_covariate <- summary_mod$coefficients[2, "Pr(>|t|)"]

# Calculate 95% Confidence Interval
# Critical value for 95% CI under normal distribution is approximately 1.96
ci_low <- estimate_first_covariate - (1.96 * stderr_first_covariate)
ci_high <- estimate_first_covariate + (1.96 * stderr_first_covariate)

# Print the results
cat("Estimate for the first covariate:", estimate_first_covariate, "\n")
cat("95% CI for the first covariate: [", ci_low, ",", ci_high, "]\n")

dat_b2 <- merge(csv_files[["b2"]], pheno, by = "SOL_ID")
dat_b2 <- dat_b2[!is.na(dat_b2[[outcomes]]),]
size_b2 <- nrow(dat_b2)

mod_df <- data.frame(Exposures = outcomes, Sample_Size = nrow(dat_list[["dat_b1"]]), Sample_Size_b2 = size_b2, Est = estimate_first_covariate,
                     CI_Lower = ci_low, CI_Upper = ci_high,
                     P_Value = pvalue_first_covariate, Metabolites = length(mrs_coefs))
result_list[[outcomes]] <- mod_df
```

# SLEA6

## Read data
```{r}

csv_files <- list()

csv_files[["b1"]] <- readRDS("Processed_metab_b1_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b1"]]), grep("SOL_ID", colnames(csv_files[["b1"]])))
colnames(csv_files[["b1"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b1"]])[col_chems])

csv_files[["b2"]] <- readRDS("Processed_metab_b2_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b2"]]), grep("SOL_ID", colnames(csv_files[["b2"]])))
colnames(csv_files[["b2"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b2"]])[col_chems])

rankNorm <- function(x){
  qnorm((rank(x, ties.method = "random", na.last = "keep")-0.5)/length(!is.na(x)))
}

chem_columns <- grep("chem", colnames(csv_files[["b1"]]), value = TRUE)

set.seed(89)
for (i in 1:length(chem_columns)){
  chem_i <- chem_columns[i]
  csv_files[["b1"]][,chem_i] <- rankNorm(csv_files[["b1"]][,chem_i])

  csv_files[["b2"]][,chem_i] <- rankNorm(csv_files[["b2"]][,chem_i])
}


pheno <- read.csv("metsleep_covariates_20200715.csv")
pheno <- lapply(pheno, function(x) ifelse(x == "", NA, x))
pheno <- as.data.frame(pheno)
pheno$SLEA4 <- as.numeric(as.character(pheno$SLEA4))
pheno$SLEA5 <- as.numeric(as.character(pheno$SLEA5))
pheno$SLEA6 <- as.numeric(as.character(pheno$SLEA6))
pheno$SLEA7 <- as.numeric(as.character(pheno$SLEA7))


##############################
####### Outcome Define #######


outcomes <- c("SLEA6")

##############################
##############################

covariates <- c("AGE", "GENDER", "CENTER", "Background")
pheno$CENTER <- factor(pheno$CENTER)
pheno$GENDER <- factor(pheno$GENDER)
pheno$Background <- factor(pheno$BKGRD1_C7)

design_vars <- c("ID", "STRAT", "PSU_ID", "WEIGHT_FINAL_NORM_OVERALL")

pheno <- pheno[,c(design_vars, outcomes, covariates)]
pheno <- pheno[!duplicated(pheno$ID),]

pheno$SOL_ID  <- as.character(pheno$ID)
```

## Batch 1

### Process Data
```{r}
dat_list <- list()

dat_list[["dat_b1"]] <- merge(pheno, csv_files[["b1"]], by = "SOL_ID", all.y = TRUE)

chem_columns <- grep("chem", colnames(dat_list[[1]]), value = TRUE)

process_data <- function(data, chem_columns) {
  data <- data[, c("SOL_ID", outcomes, "AGE", "GENDER",
                   "CENTER", "Background", chem_columns)]
  data <- data[complete.cases(data),]
  data$CENTER <- as.factor(data$CENTER)
  data$Background <- as.factor(data$Background)
  return(data)
}
dat_list[["dat_b1"]] <- process_data(dat_list[["dat_b1"]], chem_columns)
```

### LASSO
```{r}
lasso_selected <- function(data, chem_columns, outcome = outcomes) {
  x <- model.matrix(as.formula(paste(outcome, "~", paste(setdiff(colnames(data), c("SOL_ID", outcome)), collapse = "+"))), data = data)
  y <- data[,outcome]
  
  # apply penalty only on metabolites and not on other variables
  n_chem <- length(chem_columns)
  p.fac = c(rep(0, ncol(x) - n_chem), rep(1, n_chem))
  
  # CV
  set.seed(1997)
  kcvlasso <- cv.glmnet(x, y, nfolds = 5,
                        family = "gaussian",
                        type.measure = "mse",
                        penalty.factor = p.fac)
  
  ind_min <- which.min(kcvlasso$cvm)
  selected_lambda <- kcvlasso$lambda[ind_min]
  
  # lasso without cross validation
  set.seed(1997)
  lasso <- glmnet(x, y,
                  lambda = selected_lambda,
                  family = "gaussian",
                  type.measure = "mse",
                  penalty.factor = p.fac)
  
  lasso_beta <- lasso$beta
  mrs_coefs <- lasso_beta[grep("chem", rownames(lasso_beta)), "s0"]
  mrs_coefs <- mrs_coefs[which(mrs_coefs != 0)]
  
  return(mrs_coefs)
}

mrs_coefs <- lasso_selected(dat_list[[1]], chem_columns)

cat("There are ", length(mrs_coefs), " metablites selected into the MRS \n")

coef_list[[outcomes]] <- mrs_coefs
chem_list[[outcomes]] <- names(mrs_coefs)
```

### Construct MRS
```{r}
compute_mrs <- function(dataset, coef_set){
  row.names(dataset) <- dataset$SOL_ID
  tmp <- as.matrix(dataset[, names(coef_set)]) %*% coef_set
  colnames(tmp) <- outcomes
  tmp <- data.frame(tmp)
  tmp$SOL_ID <- rownames(tmp)
  mrs_b2 <- tmp
  row.names(mrs_b2) <- NULL
  return(mrs_b2)
}

mrs_b2 <- compute_mrs(csv_files[["b2"]], mrs_coefs)


# standardize MRS

mrs_b2[, 1] <- as.vector(scale(mrs_b2[, 1]))
colnames(mrs_b2)[1] <- paste0(outcomes, "_MRS")
```

### Association Test
```{r}
mod <- sol_association_analysis(pheno = pheno, mrs_df = mrs_b2, id_col = "SOL_ID", outcome = outcomes,
                            cov_names = covariates, family_type = "gaussian")
```

### store value
```{r}
summary_mod <- summary(mod)

# Extract Estimate and Standard Error for the first covariate
# The first covariate is at position 2 (as position 1 is the intercept)
estimate_first_covariate <- summary_mod$coefficients[2, "Estimate"]
stderr_first_covariate <- summary_mod$coefficients[2, "Std. Error"]
pvalue_first_covariate <- summary_mod$coefficients[2, "Pr(>|t|)"]

# Calculate 95% Confidence Interval
# Critical value for 95% CI under normal distribution is approximately 1.96
ci_low <- estimate_first_covariate - (1.96 * stderr_first_covariate)
ci_high <- estimate_first_covariate + (1.96 * stderr_first_covariate)

# Print the results
cat("Estimate for the first covariate:", estimate_first_covariate, "\n")
cat("95% CI for the first covariate: [", ci_low, ",", ci_high, "]\n")

dat_b2 <- merge(csv_files[["b2"]], pheno, by = "SOL_ID")
dat_b2 <- dat_b2[!is.na(dat_b2[[outcomes]]),]
size_b2 <- nrow(dat_b2)

mod_df <- data.frame(Exposures = outcomes, Sample_Size = nrow(dat_list[["dat_b1"]]), Sample_Size_b2 = size_b2, Est = estimate_first_covariate,
                     CI_Lower = ci_low, CI_Upper = ci_high,
                     P_Value = pvalue_first_covariate, Metabolites = length(mrs_coefs))
result_list[[outcomes]] <- mod_df
```

# SLEA7

## Read data
```{r}

csv_files <- list()

csv_files[["b1"]] <- readRDS("Processed_metab_b1_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b1"]]), grep("SOL_ID", colnames(csv_files[["b1"]])))
colnames(csv_files[["b1"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b1"]])[col_chems])

csv_files[["b2"]] <- readRDS("Processed_metab_b2_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b2"]]), grep("SOL_ID", colnames(csv_files[["b2"]])))
colnames(csv_files[["b2"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b2"]])[col_chems])

rankNorm <- function(x){
  qnorm((rank(x, ties.method = "random", na.last = "keep")-0.5)/length(!is.na(x)))
}

chem_columns <- grep("chem", colnames(csv_files[["b1"]]), value = TRUE)

set.seed(89)
for (i in 1:length(chem_columns)){
  chem_i <- chem_columns[i]
  csv_files[["b1"]][,chem_i] <- rankNorm(csv_files[["b1"]][,chem_i])

  csv_files[["b2"]][,chem_i] <- rankNorm(csv_files[["b2"]][,chem_i])
}


pheno <- read.csv("metsleep_covariates_20200715.csv")
pheno <- lapply(pheno, function(x) ifelse(x == "", NA, x))
pheno <- as.data.frame(pheno)
pheno$SLEA4 <- as.numeric(as.character(pheno$SLEA4))
pheno$SLEA5 <- as.numeric(as.character(pheno$SLEA5))
pheno$SLEA6 <- as.numeric(as.character(pheno$SLEA6))
pheno$SLEA7 <- as.numeric(as.character(pheno$SLEA7))


##############################
####### Outcome Define #######


outcomes <- c("SLEA7")

##############################
##############################

covariates <- c("AGE", "GENDER", "CENTER", "Background")
pheno$CENTER <- factor(pheno$CENTER)
pheno$GENDER <- factor(pheno$GENDER)
pheno$Background <- factor(pheno$BKGRD1_C7)

design_vars <- c("ID", "STRAT", "PSU_ID", "WEIGHT_FINAL_NORM_OVERALL")

pheno <- pheno[,c(design_vars, outcomes, covariates)]
pheno <- pheno[!duplicated(pheno$ID),]

pheno$SOL_ID  <- as.character(pheno$ID)
```

## Batch 1

### Process Data
```{r}
dat_list <- list()

dat_list[["dat_b1"]] <- merge(pheno, csv_files[["b1"]], by = "SOL_ID", all.y = TRUE)

chem_columns <- grep("chem", colnames(dat_list[[1]]), value = TRUE)

process_data <- function(data, chem_columns) {
  data <- data[, c("SOL_ID", outcomes, "AGE", "GENDER",
                   "CENTER", "Background", chem_columns)]
  data <- data[complete.cases(data),]
  data$CENTER <- as.factor(data$CENTER)
  data$Background <- as.factor(data$Background)
  return(data)
}
dat_list[["dat_b1"]] <- process_data(dat_list[["dat_b1"]], chem_columns)
```

### LASSO
```{r}
lasso_selected <- function(data, chem_columns, outcome = outcomes) {
  x <- model.matrix(as.formula(paste(outcome, "~", paste(setdiff(colnames(data), c("SOL_ID", outcome)), collapse = "+"))), data = data)
  y <- data[,outcome]
  
  # apply penalty only on metabolites and not on other variables
  n_chem <- length(chem_columns)
  p.fac = c(rep(0, ncol(x) - n_chem), rep(1, n_chem))
  
  # CV
  set.seed(1997)
  kcvlasso <- cv.glmnet(x, y, nfolds = 5,
                        family = "gaussian",
                        type.measure = "mse",
                        penalty.factor = p.fac)
  
  ind_min <- which.min(kcvlasso$cvm)
  selected_lambda <- kcvlasso$lambda[ind_min]
  
  # lasso without cross validation
  set.seed(1997)
  lasso <- glmnet(x, y,
                  lambda = selected_lambda,
                  family = "gaussian",
                  type.measure = "mse",
                  penalty.factor = p.fac)
  
  lasso_beta <- lasso$beta
  mrs_coefs <- lasso_beta[grep("chem", rownames(lasso_beta)), "s0"]
  mrs_coefs <- mrs_coefs[which(mrs_coefs != 0)]
  
  return(mrs_coefs)
}

mrs_coefs <- lasso_selected(dat_list[[1]], chem_columns)

cat("There are ", length(mrs_coefs), " metablites selected into the MRS \n")

coef_list[[outcomes]] <- mrs_coefs
chem_list[[outcomes]] <- names(mrs_coefs)
```

### Construct MRS
```{r}
compute_mrs <- function(dataset, coef_set){
  row.names(dataset) <- dataset$SOL_ID
  tmp <- as.matrix(dataset[, names(coef_set)]) %*% coef_set
  colnames(tmp) <- outcomes
  tmp <- data.frame(tmp)
  tmp$SOL_ID <- rownames(tmp)
  mrs_b2 <- tmp
  row.names(mrs_b2) <- NULL
  return(mrs_b2)
}

mrs_b2 <- compute_mrs(csv_files[["b2"]], mrs_coefs)


# standardize MRS

mrs_b2[, 1] <- as.vector(scale(mrs_b2[, 1]))
colnames(mrs_b2)[1] <- paste0(outcomes, "_MRS")
```

### Association Test
```{r}
mod <- sol_association_analysis(pheno = pheno, mrs_df = mrs_b2, id_col = "SOL_ID", outcome = outcomes,
                            cov_names = covariates, family_type = "gaussian")
```

### store value
```{r}
summary_mod <- summary(mod)

# Extract Estimate and Standard Error for the first covariate
# The first covariate is at position 2 (as position 1 is the intercept)
estimate_first_covariate <- summary_mod$coefficients[2, "Estimate"]
stderr_first_covariate <- summary_mod$coefficients[2, "Std. Error"]
pvalue_first_covariate <- summary_mod$coefficients[2, "Pr(>|t|)"]

# Calculate 95% Confidence Interval
# Critical value for 95% CI under normal distribution is approximately 1.96
ci_low <- estimate_first_covariate - (1.96 * stderr_first_covariate)
ci_high <- estimate_first_covariate + (1.96 * stderr_first_covariate)

# Print the results
cat("Estimate for the first covariate:", estimate_first_covariate, "\n")
cat("95% CI for the first covariate: [", ci_low, ",", ci_high, "]\n")

dat_b2 <- merge(csv_files[["b2"]], pheno, by = "SOL_ID")
dat_b2 <- dat_b2[!is.na(dat_b2[[outcomes]]),]
size_b2 <- nrow(dat_b2)

mod_df <- data.frame(Exposures = outcomes, Sample_Size = nrow(dat_list[["dat_b1"]]), Sample_Size_b2 = size_b2, Est = estimate_first_covariate,
                     CI_Lower = ci_low, CI_Upper = ci_high,
                     P_Value = pvalue_first_covariate, Metabolites = length(mrs_coefs))
result_list[[outcomes]] <- mod_df
```


# SLEA11

## Read data
```{r}

csv_files <- list()

csv_files[["b1"]] <- readRDS("Processed_metab_b1_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b1"]]), grep("SOL_ID", colnames(csv_files[["b1"]])))
colnames(csv_files[["b1"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b1"]])[col_chems])

csv_files[["b2"]] <- readRDS("Processed_metab_b2_updated.RDS")
col_chems <- setdiff(1:ncol(csv_files[["b2"]]), grep("SOL_ID", colnames(csv_files[["b2"]])))
colnames(csv_files[["b2"]])[col_chems] <- paste0("chem_", colnames(csv_files[["b2"]])[col_chems])

rankNorm <- function(x){
  qnorm((rank(x, ties.method = "random", na.last = "keep")-0.5)/length(!is.na(x)))
}

chem_columns <- grep("chem", colnames(csv_files[["b1"]]), value = TRUE)

set.seed(89)
for (i in 1:length(chem_columns)){
  chem_i <- chem_columns[i]
  csv_files[["b1"]][,chem_i] <- rankNorm(csv_files[["b1"]][,chem_i])

  csv_files[["b2"]][,chem_i] <- rankNorm(csv_files[["b2"]][,chem_i])
}


pheno <- read.csv("metsleep_covariates_20200715.csv")
pheno <- lapply(pheno, function(x) ifelse(x == "", NA, x))
pheno <- as.data.frame(pheno)
pheno$SLEA4 <- as.numeric(as.character(pheno$SLEA4))
pheno$SLEA5 <- as.numeric(as.character(pheno$SLEA5))
pheno$SLEA6 <- as.numeric(as.character(pheno$SLEA6))
pheno$SLEA7 <- as.numeric(as.character(pheno$SLEA7))
pheno$SLEA11 <- as.numeric(as.character(pheno$SLEA11))


##############################
####### Outcome Define #######


outcomes <- c("SLEA11")

##############################
##############################

covariates <- c("AGE", "GENDER", "CENTER", "Background")
pheno$CENTER <- factor(pheno$CENTER)
pheno$GENDER <- factor(pheno$GENDER)
pheno$Background <- factor(pheno$BKGRD1_C7)

design_vars <- c("ID", "STRAT", "PSU_ID", "WEIGHT_FINAL_NORM_OVERALL")

pheno <- pheno[,c(design_vars, outcomes, covariates)]
pheno <- pheno[!duplicated(pheno$ID),]

pheno$SOL_ID  <- as.character(pheno$ID)
```

## Batch 1

### Process Data
```{r}
dat_list <- list()

dat_list[["dat_b1"]] <- merge(pheno, csv_files[["b1"]], by = "SOL_ID", all.y = TRUE)

chem_columns <- grep("chem", colnames(dat_list[[1]]), value = TRUE)

process_data <- function(data, chem_columns) {
  data <- data[, c("SOL_ID", outcomes, "AGE", "GENDER",
                   "CENTER", "Background", chem_columns)]
  data <- data[complete.cases(data),]
  data$CENTER <- as.factor(data$CENTER)
  data$Background <- as.factor(data$Background)
  return(data)
}
dat_list[["dat_b1"]] <- process_data(dat_list[["dat_b1"]], chem_columns)
```

### LASSO
```{r}
lasso_selected <- function(data, chem_columns, outcome = outcomes) {
  x <- model.matrix(as.formula(paste(outcome, "~", paste(setdiff(colnames(data), c("SOL_ID", outcome)), collapse = "+"))), data = data)
  y <- data[,outcome]
  
  # apply penalty only on metabolites and not on other variables
  n_chem <- length(chem_columns)
  p.fac = c(rep(0, ncol(x) - n_chem), rep(1, n_chem))
  
  # CV
  set.seed(1997)
  kcvlasso <- cv.glmnet(x, y, nfolds = 5,
                        family = "gaussian",
                        type.measure = "mse",
                        penalty.factor = p.fac)
  
  ind_min <- which.min(kcvlasso$cvm)
  selected_lambda <- kcvlasso$lambda[ind_min]
  
  # lasso without cross validation
  set.seed(1997)
  lasso <- glmnet(x, y,
                  lambda = selected_lambda,
                  family = "gaussian",
                  type.measure = "mse",
                  penalty.factor = p.fac)
  
  lasso_beta <- lasso$beta
  mrs_coefs <- lasso_beta[grep("chem", rownames(lasso_beta)), "s0"]
  mrs_coefs <- mrs_coefs[which(mrs_coefs != 0)]
  
  return(mrs_coefs)
}

mrs_coefs <- lasso_selected(dat_list[[1]], chem_columns)

cat("There are ", length(mrs_coefs), " metablites selected into the MRS \n")

coef_list[[outcomes]] <- mrs_coefs
chem_list[[outcomes]] <- names(mrs_coefs)
```

### Construct MRS
```{r}
compute_mrs <- function(dataset, coef_set){
  row.names(dataset) <- dataset$SOL_ID
  tmp <- as.matrix(dataset[, names(coef_set)]) %*% coef_set
  colnames(tmp) <- outcomes
  tmp <- data.frame(tmp)
  tmp$SOL_ID <- rownames(tmp)
  mrs_b2 <- tmp
  row.names(mrs_b2) <- NULL
  return(mrs_b2)
}

mrs_b2 <- compute_mrs(csv_files[["b2"]], mrs_coefs)


# standardize MRS

mrs_b2[, 1] <- as.vector(scale(mrs_b2[, 1]))
colnames(mrs_b2)[1] <- paste0(outcomes, "_MRS")
```

### Association Test
```{r}
mod <- sol_association_analysis(pheno = pheno, mrs_df = mrs_b2, id_col = "SOL_ID", outcome = outcomes,
                            cov_names = covariates, family_type = "gaussian")
```

### store value
```{r}
summary_mod <- summary(mod)

# Extract Estimate and Standard Error for the first covariate
# The first covariate is at position 2 (as position 1 is the intercept)
estimate_first_covariate <- summary_mod$coefficients[2, "Estimate"]
stderr_first_covariate <- summary_mod$coefficients[2, "Std. Error"]
pvalue_first_covariate <- summary_mod$coefficients[2, "Pr(>|t|)"]

# Calculate 95% Confidence Interval
# Critical value for 95% CI under normal distribution is approximately 1.96
ci_low <- estimate_first_covariate - (1.96 * stderr_first_covariate)
ci_high <- estimate_first_covariate + (1.96 * stderr_first_covariate)

# Print the results
cat("Estimate for the first covariate:", estimate_first_covariate, "\n")
cat("95% CI for the first covariate: [", ci_low, ",", ci_high, "]\n")

dat_b2 <- merge(csv_files[["b2"]], pheno, by = "SOL_ID")
dat_b2 <- dat_b2[!is.na(dat_b2[[outcomes]]),]
size_b2 <- nrow(dat_b2)

mod_df <- data.frame(Exposures = outcomes, Sample_Size = nrow(dat_list[["dat_b1"]]), Sample_Size_b2 = size_b2, Est = estimate_first_covariate,
                     CI_Lower = ci_low, CI_Upper = ci_high,
                     P_Value = pvalue_first_covariate, Metabolites = length(mrs_coefs))
result_list[[outcomes]] <- mod_df
```

# Table
```{r}
tab_temp <- do.call(rbind, result_list)
tab_report <- tab_temp %>%
  mutate(
    Est = round(Est, 4),
    CI = paste0("[", round(CI_Lower, 4), ", ", round(CI_Upper, 4), "]"),
    P_Value = sprintf("%.4e", P_Value)
  ) %>%
  select(Exposures, Sample_Size, Sample_Size_b2, Est, CI, P_Value, Metabolites) # Reorder columns

write.csv(tab_report, "Results/20240616_MRS_results_M1_Ranked_V3.csv", row.names = FALSE)
saveRDS(tab_temp, "Results/20240616_MRS_forPlot_M1_Ranked_V2.RDS")
```


# Upset Diagram
```{r}
count_list <- list()
labels <- c()
for (i in names(chem_list)) {
  count_list[[i]] <- length(chem_list[[i]])
  labels <- c(labels, paste(i, "(n=", count_list[[i]], ")", sep = ""))
}

all_chemicals <- sort(unique(unlist(chem_list)))
binary_data <- sapply(chem_list, function(set, all_chems) {
    as.integer(all_chems %in% set)
}, all_chems = all_chemicals)
colnames(binary_data) <- names(chem_list)
binary_df <- as.data.frame(binary_data)
binary_df$chemicals <- all_chemicals

upset_plot <- upset(binary_df, sets = names(chem_list), text.scale = c(2, 2, 2, 2, 2, 2))
#saveRDS(binary_df, "20240312_MRS_Metabolites_Overlap_M1_Ranked.RDS")
```


# Coef Table
```{r}
coef_table_list <- list()
for (i in names(coef_list)) {
  tab_temp <- as.data.frame(coef_list[[i]])
  colnames(tab_temp) <- i
  tab_temp <- data.frame('CHEM_ID' = rownames(tab_temp), tab_temp)
  rownames(tab_temp) <- NULL
  coef_table_list[[i]] <- tab_temp
}


chem_id <- chem_columns
com_mat <- data.frame(CHEM_ID = chem_id)

metab_batch2_file <- file.path("batch2_data.xlsx")
metabolites_info_sheet_name <- "metabolites.info"

metab_info <- as.data.frame(read_excel(metab_batch2_file, sheet = metabolites_info_sheet_name))
metab_info$CHEM_ID <- paste0("chem_", metab_info$CHEM_ID)

com_mat <- merge(com_mat, metab_info[,c("CHEM_ID","CHEMICAL_NAME", "HMDB")], 
                    by = "CHEM_ID")


com_mat <- reduce(coef_table_list, ~left_join(.x, .y, by = "CHEM_ID"), .init = com_mat)
com_mat[, 4:ncol(com_mat)][is.na(com_mat[, 4:ncol(com_mat)])] <- 0
write.csv(com_mat, "Results/20240616_MRS_Coef_M1_Ranked_V2.csv", row.names = FALSE)
```








